### 2019-03-16 README.Rmd
Misc cleanup

**citesdb** is a package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 20 million records of reported shipments of wildlife and wildlife
products subject to oversight under the Convention on International Trade in Endangered Species.

@@

Not to worry, just do as it says and run `cites_db_download()`.  This will
fetch the most recent database from online, an approximately 158 MB download.
It will expand to over 1 GB in the local database. During
the downloaad and database building up to 3.5 GB of disk space may be used temporarily.

@@

The back-end database, [MonetDB](https://monetdb.org) is very fast and powerful, making such
analyses quite snappy even on such large data using normal desktops and laptops. Here's the
timing of the above query, which procecses over 20 million records, on an ordinary laptop:

@@

If you are using a recent version of RStudio interactively, loading the CITES package also brings
up a browsable pane in the "Connections" tab that lets you explore and preview
the database, as well as interact with it direcctly via SQL commands.

@@

[![EcoHealth Allinace](https://github.com/ecohealthalliance/citesdb/blob/master/inst/img/eha-footer.png)](https://www.ecohealthalliance.org/)

>>>>

**citesdb** is a package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 20 million records of reported shipments of wildlife and wildlife
products subject to oversight under the [Convention on International Trade in Endangered Species of Wild Fauna and Flora](https://www.cites.org)

@@

Not to worry, just do as it says and run `cites_db_download()`.  This will
fetch the most recent database from online, an approximately 158 MB download.
It will expand to over 1 GB in the local database. During
the download and database building up to 3.5 GB of disk space may be used temporarily.

@@

The back-end database, [MonetDB](https://monetdb.org) is very fast and powerful, making such
analyses quite snappy even on such large data using normal desktops and laptops. Here's the
timing of the above query, which processes over 20 million records, on an ordinary laptop:

@@

If you are using a recent version of RStudio interactively, loading the CITES package also brings
up a browsable pane in the "Connections" tab that lets you explore and preview
the database, as well as interact with it directly via SQL commands.

@@

[![Created by EcoHealth Alliance](https://github.com/ecohealthalliance/citesdb/blob/master/inst/img/eha-footer.png)](https://www.ecohealthalliance.org/)
